DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/evaluation.tex
..

In each experiment, we run a single DNN model one core, and
co-scheduled an increasing number of the memory intensive synthetic
benchmarks~\footnote{We use the \emph{Bandwidth} benchmark in the
  IsolBench suite, with the following command line parameters: \texttt{\$
  bandwdith -a write -m 16384}}, on the remaining idle cores.

>>>>

We run a single DNN model one core, and
co-schedule an increasing number of the memory intensive synthetic
benchmarks~\footnote{We use the \emph{Bandwidth} benchmark in the
  IsolBench suite, with the following command line parameters: \texttt{\$
  bandwdith -a write -m 16384}}, on the remaining idle cores.
